Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-04 sections/03-trending.tex
Update on Overleaf.

As outlined in Section~\ref{sec:introduction}, we refer by trending to the consistency of an observed change with the change issued by another measurement, a nowcast, or a forecast.
In this section, we want to specify trending and lay out different methods of measuring and visualizing trending. 
In general, trending can be assessed for different lags $l$ separately, and the relevance of considered lags has to be determined based on the question at hand.
Throughout the section, we call a measurement, nowcast, or forecast a \textit{prediction} or \textit{signal}.
Before introducing measures for assessing trending, we give remarks on computing the predicted change and notation in Section~\ref{subsec:notation}.
The remainder of the section is structured as follows.
Section~\ref{subsec:trending-basics} introduces trending basics and visualizes trending in a synthetical example.
Section~\ref{subsec:trending-measures} reviews conveyed quantification approaches from other fields.
The approaches are extended to the trending setting in Section~\ref{subsec:trending-noise}.
Section~\ref{subsec:trending-cond-prob} introduces a new graphical method of trending assessment and briefly introduces bootstrap methods for computing confidence intervals for the measures.

>>>>

As outlined in Section~\ref{sec:introduction}, we refer by trending to the consistency of an observed change with the change issued by another measurement, a nowcast, or a forecast.
In this section, we want to specify trending and lay out different methods of measuring and visualizing trending. 
In general, trending can be assessed for different lags $l$ separately, and the relevance of the considered lags has to be determined based on the question at hand.
Throughout the section, we call a measurement, nowcast, or forecast a \textit{prediction} or \textit{signal} whenever the application area is insignificant.
Before introducing measures for assessing trending, we give remarks on computing the predicted change and notation in Section~\ref{subsec:notation}.
Section~\ref{subsec:trending-basics} introduces trending basics and visualizes trending in a synthetical example.
In Section~\ref{subsec:trending-measures}, various quantification methods from different disciplines and tasks are examined.
The approaches are extended to the trending setting in Section~\ref{subsec:trending-noise}.
Section~\ref{subsec:trending-cond-prob} introduces a new graphical method of trending assessment and briefly introduces bootstrap methods for computing confidence intervals for the measures.
